Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-11 emsoft-2019/related.tex
removing comment on related work

\citet{Abate2017} design safe feedback controllers with counterexample guided
inductive synthesis (CEGIS). Safety verification needs to consider quantization
errors in the controller and in the plant model as the algorithm is based on
bounded model checking (BMC) and tracks roundoff errors with interval
arithmetic. While this algorithm generates the controller and its
implementation, due to limitations in BMC it only considers uniform fixed-point
word length in steps of 8.
\eva{I guess it also does not consider robustness? Not sure how this is related.}
\Sadegh{Eva, You explanation is good. I think the way we look at the problem is different from \cite{Abate2017}: \cite{Abate2017} assumes a fixed precision is given and tries to design the controller with the specific precision such that the safety constraints are satisfied, so no discussion on robustness or memory usage. In our case we don't fix a precision. We find a controller together with a mixed precision that satisfies the constraints and respects the memory budget.}

>>>>

\citet{Abate2017} design safe feedback controllers with counterexample guided
inductive synthesis (CEGIS). Safety verification needs to consider quantization
errors in the controller and in the plant model as the algorithm is based on
bounded model checking (BMC) and tracks roundoff errors with interval
arithmetic. While this algorithm generates the controller and its
implementation, due to limitations in BMC it only considers uniform fixed-point
word length in steps of 8.
% \eva{I guess it also does not consider robustness? Not sure how this is related.}
% \Sadegh{Eva, You explanation is good. I think the way we look at the problem is different from \cite{Abate2017}: \cite{Abate2017} assumes a fixed precision is given and tries to design the controller with the specific precision such that the safety constraints are satisfied, so no discussion on robustness or memory usage. In our case we don't fix a precision. We find a controller together with a mixed precision that satisfies the constraints and respects the memory budget.}
